%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% MASTER THESIS
%
% This is the main .tex-document for my master thesis.
% In here only belong necessary things, such as the declaration of the document class.
% Everything else is supposed to be in seperate files which are then included via \input.
% Have fun writing!
%
% Fabian Burghart, 2018/02/17
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\RequirePackage[l2tabu, orthodox]{nag}
\documentclass[a4paper,11pt,twoside,notitlepage]{report}
\usepackage[a4paper, inner=3cm, outer=2cm, top=3cm, bottom=3cm]{geometry}

\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{lmodern}

% Remaining packages %
\input{mt_preamble_packages.tex}


% Options and shortcuts %
\input{mt_preamble_options.tex}


% Bibliography
\addbibresource{mt_bib.bib}

% Title Page

\title{$\ $\\ \textsc{The Einstein Relation on Fractals and Other Singular Sets}\\$\ $}
\author{{\Large {Fabian Burghart}}\\[1em]
  {\large April 2, 2018}\\[10em]}
\date{{\large Master thesis in mathematics}\\
  {\large Advisor: Prof. Dr. Uta Renata Freiberg}\\[7em]
  {\large \textsc{Fakult{\"a}t f{\"u}r Mathematik und Physik der Universit{\"a}t Stuttgart}}} 

%%%%%%%%%%%%%%
%% DOCUMENT %%
%%%%%%%%%%%%%%

\begin{document}
\maketitle
\thispagestyle{empty}
\newpage

\thispagestyle{empty}

\section*{Preface: Beware of construction works!}

This is an early draft of my Master thesis on the so-called Einstein relation. ``Early'' because I started working on the topic after the German winter term finished (which was mid-February at my university) and since spent most of my time reading literature to understand the existing theory. Accordingly, a lot of the ideas I currently have are not yet worked out completely, a lot of the text is still unrefined, pictures for the examples in chapter 2 are non-existent, there are several gaps in the material that still have to be filled out - and even the title might be subject to future changes. However, I added short remarks denoted by ``TO DO'' to signify my overall plans, and I do hope that this current draft - despite admittedly resembling a desolate construction site more than a newly finished building - fulfills the needs as part of this application.

\begin{flushright}
  Fabian Burghart, 2nd April 2018. 
\end{flushright}


\tableofcontents


% Chapter I. An introduction to the Einstein Relation
\include{mt_ch1}

% Chapter II. Examples and Non-examples
\include{mt_ch2}

%Chapter III.
\include{mt_ch3}

% Bibliography

\nocite{*}   %CAUTION!!!

\printbibliography
\addcontentsline{toc}{chapter}{Bibliography}


\end{document} 


